---
title: "Old files testing"
author: "Jose Luis Delgado Davara"
date: "5/30/2018"
output:
  html_document: default
  pdf_document: default
---

This file checks discrepancies between the two files GovData and GovDataIND of the 2017 ingestion.

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
```

```{r Read files}
Data2017 = read.csv("../Ingestion Fall 2017 - Regina Files/GovData360.csv", sep = ";")
DataIND2017 = read.csv("../Ingestion Fall 2017 - Regina Files/GovData360IND.csv", sep = ";")
```

### Indicators in the values file not registered in the Indicators file

```{r}
setdiff(unique(Data2017$Indicator_Id), unique(DataIND2017$Indicator_Id))
```
All indicators in the values file are registered in the indicators file.

### Indicators in the IND file not registered in the values file

```{r}
notmatched.indicators = setdiff(unique(DataIND2017$Indicator_Id), unique(Data2017$Indicator_Id))
print(notmatched.indicators)
```

**There are 459 indicators in the Fall 2017 ingestion that do not match in the two files. The INDICATORS files have more that the values file.**

### Data sources with inconsistencies

```{r}
Sources = gsub("[[:digit:]]", "", notmatched.indicators)
print('List of data sources with inconsintencies and number of inconsistencies:')
table(Sources)
```



