---
title: "Create GovData and GovDataIND"
author: "Jose Luis Delgado Davara"
date: "5/21/2018"
output: html_document
---

This Rmarkdown is used to prepare the final files to send. This means:

1. Join vertically all the updated files --> INDupdates2018.csv and updates_2018.csv
2. Filter out the indicators without category assigned. From both IND and values files. (Drop.csv file)
3. Get the not-updated indicators and values from previous ingestion (GovData2017 and GovData2017IND)
4. Join vertically the files from (1) and (2) with the ones in (3)
5. Clean, match and fix legacy problems

```{r libraries, include=FALSE}
library(dplyr)
library(stringr)
library(data.table)
```

## 1) Join Vertically updated files.

```{r}
SOURCES2018 = c("BTI", "DB", "CPIA", "FH", "GCI", "IIAG", "ILO", "IPD", "IPU", "PEFA", "SC", "SGI", "TI", "WBL", "WGI", "WJP")

TRIAL = 'PEFA'

INDupdates2018 <- as.data.frame(matrix(ncol=0, nrow=0))
updates2018 <- as.data.frame(matrix(ncol=0, nrow=0))
for (i in SOURCES2018){
  if (!(i %in% (c("PEFA", "WBL")))){ #PEFA and WBL contains encoded values. Done later
    # Read files
    Route = paste0("1 Data cleaning/Cleaned files/",i,".csv")
    Route_IND = paste0("1 Data cleaning/Cleaned files/",i,"IND.csv")
    df = read.csv(Route, sep = ",")
    df_IND = read.csv(Route_IND, sep = ",")
     
    print(i)
    print(paste0("Number of columns imported in the .csv: ", ncol(df)))
    print(paste0("Number of columns imported in the IND.csv: ", ncol(df_IND)))
    #print(colnames(df_IND))
    INDupdates2018 = rbind(INDupdates2018, df_IND)
    updates2018 = rbind(updates2018, df)
  }
}  
dim(INDupdates2018)
dim(updates2018)

#PEFA and WBL has a column colled 'Encoded'.
# Create 'Encoded' column
updates2018$encoded = ''

Route = "1 Data cleaning/Cleaned files/PEFA.csv"
Route_IND = "1 Data cleaning/Cleaned files/PEFAIND.csv"
df_PEFA = read.csv(Route, sep = ",")
df_PEFA$encoded = ''
df_IND_PEFA = read.csv(Route_IND, sep = ",")

Route = "1 Data cleaning/Cleaned files/WBL.csv"
Route_IND = "1 Data cleaning/Cleaned files/WBLIND.csv"
df_WBL = read.csv(Route, sep = ",")
df_IND_WBL = read.csv(Route_IND, sep = ",")

# Join vertically PEFA
INDupdates2018 = rbind(INDupdates2018, df_IND_PEFA, df_IND_WBL)
updates2018 = rbind(updates2018, df_PEFA, df_WBL)
dim(INDupdates2018)
dim(updates2018)
```

## 2) Filter out the indicators without category assigned.

```{r filter not selected indicators from IND}
# Remove those without category from the IND file
INDupdates2018 = INDupdates2018 %>% filter(is.na(Value_Type_Slug) == F)
dim(INDupdates2018)
```

```{r Remove duplicated}
List.of.indicators = INDupdates2018$Indicator_Id
length(unique(List.of.indicators)) # There are 31 of them duplicated

List.of.indicators = as.data.frame(List.of.indicators)
duplicated.indicators = List.of.indicators[duplicated(List.of.indicators), ]

# filter out the duplicated values
INDupdates2018 = INDupdates2018[!(INDupdates2018$Indicator_Id %in% duplicated.indicators), ]
updates2018 = updates2018[!(updates2018$Indicator_Id %in% duplicated.indicators), ]

List.of.indicators = INDupdates2018$Indicator_Id
# --> See note at the end of this chuck
```

It seems that some of the indicators of WJP have been duplicated for different years. This is probably because they changed the name. -> Solution: consolidate them.

In DB, one of the indicators was deleted and I was unable to identificate it previously, so it was assigned again with another code. -> Solution: delete it.

duplicated.indicators
 [1] 66-DB-Total  45-DB-Total  71-WJP-Total 38-WJP-Total
 [5] 67-WJP-Total 39-WJP-Total 66-WJP-Total 33-WJP-Total
 [9] 1-WJP-Total  27-WJP-Total 60-WJP-Total 40-WJP-Total
[13] 65-WJP-Total 57-WJP-Total 48-WJP-Total 56-WJP-Total
[17] 49-WJP-Total 50-WJP-Total 55-WJP-Total 54-WJP-Total
[21] 51-WJP-Total 47-WJP-Total 58-WJP-Total 23-WJP-Total
[25] 76-WJP-Total 68-WJP-Total 37-WJP-Total 75-WJP-Total
[29] 24-WJP-Total 26-WJP-Total 73-WJP-Total 25-WJP-Total
[33] 74-WJP-Total 46-WJP-Total 59-WJP-Total

```{r filter in the values dataset and in the indicators}
# Filter in values dataset, the indicators in df_IND
updates2018 = updates2018[(updates2018$Indicator_Id %in% List.of.indicators), ]
length(unique(updates2018$Indicator_Id))

# Filter in IND dataset, the not duplicated indicators
INDupdates2018 = INDupdates2018[(INDupdates2018$Indicator_Id %in% List.of.indicators), ]
length(unique(INDupdates2018$Indicator_Id))
```

## 3) Get the not-updated indicators and values from previous ingestion (GovData2017 and GovData2017IND)

```{r Read old files}
# Read 2017 files
GovData2017 = read.csv("../big files/GovData360.csv", sep = ",")
GovDataIND2017 = read.csv("Data preprocessed/GovData360IND.csv", sep = ";")
# Filter out the not updated ones
GovData2017 = GovData2017[!(GovData2017$dataset %in% SOURCES2018), ]
GovDataIND2017 = GovDataIND2017[!(GovDataIND2017$Dataset %in% SOURCES2018), ]
```

GovData2017 and GovDataIND2017 contain the values that remain intouchable in the database.

## 4) Join vertically the files from (1) and (2) with the ones in (3)

```{r}
# ADJUST THE COLUMNS OF IND FILE
colnames(GovDataIND2017)
colnames(INDupdates2018)

INDupdates2018$Indicator_Code = INDupdates2018$Indicator_Id
GovDataIND2017$Indicator.Code = 'not-updated spring18'
GovDataIND2017$Indicator.ID = 'not-updated spring18'
GovDataIND2017$indicator = GovDataIND2017$Display_Name
#GovDataIND2017$indicator = 'not-updated in spring18'
dropIND = c('X')
INDupdates2018 = INDupdates2018[, !(names(INDupdates2018) %in% dropIND)] 
colnames(INDupdates2018)[1] = 'indicator'

  # Comprobation
setdiff(colnames(GovDataIND2017), colnames(INDupdates2018))
setdiff(colnames(INDupdates2018), colnames(GovDataIND2017))

# ADJUST THE COLUMNS OF VALUES FILE
colnames(GovData2017)[19] = 'Indicator.Code'
drop = c('keyN', 'country', 'Region', 'Incomegroup', 'Lendingcategory', 'OtherGroup', 'Indebtedness', 'D_FS', 'Indicator.Code')
GovData2017 = GovData2017[, !(names(GovData2017) %in% drop)]
colnames(GovData2017)
colnames(updates2018)[2] = 'indicator'
updates2018$Indicator_Name = updates2018$question

drop2 = c('X', 'encoded')
updates2018 = updates2018[, !(names(updates2018) %in% drop2)]

  # Comprobation
setdiff(colnames(GovData2017), colnames(updates2018))
setdiff(colnames(updates2018), colnames(GovData2017))
```

There are inconsistencies between the two files with the Indicator_Name. Let's rename the column indicator and make them consistent.
```{r Solve the Indicator_Name problem}
GovDataIND2017$indicator = GovDataIND2017$Indicator_Name
GovData2017$indicator = GovData2017$Indicator_Name
```

```{r vertical join}
# Vertical join
GovData360IND = rbind(INDupdates2018, GovDataIND2017)
GovData360 = rbind(updates2018, GovData2017)

drop = c('category_15')
GovData360 = GovData360[, !(names(GovData360) %in% drop)]
GovData360IND$overlap[is.na(GovData360IND$overlap)] = 'GOV'

setdiff(unique(GovData360$Indicator_Id), unique(GovData360IND$Indicator_Id))
setdiff(unique(GovData360IND$Indicator_Id), unique(GovData360$Indicator_Id))
```

## 5) Clean, match and fix legacy problems

After doing this, there are some legacy indicators in the IND file that are not present in the values file. 

On the other hand, there are some values with empty Indicator_Id that are not present in the IND files - These are the ones with value == 'NA'.

### Iso3
There are some erroneous country iso3 codes. Let's fix it.

```{r}
# Clean manually the ones we know are not correct
GovData360$iso3[GovData360$iso3 == 'AND'] = 'ADO'
GovData360$iso3[GovData360$iso3 == 'COD'] = 'ZAR'
GovData360$iso3[GovData360$iso3 == 'IMN'] = 'IMY'
GovData360$iso3[GovData360$iso3 == 'RCA'] = 'CAF'
GovData360$iso3[GovData360$iso3 == 'RKS'] = 'KSV'
GovData360$iso3[GovData360$iso3 == 'ROU'] = 'ROM'
GovData360$iso3[GovData360$iso3 == 'UAE'] = 'ARE'
GovData360$iso3[GovData360$iso3 == 'YUG'] = 'SRB'

ISO3 = read.csv('aux_Data/COUNTRIES_ISO3.csv', sep = ",")
ISO3 = t(ISO3)
GovData360 = GovData360[(GovData360$iso3 %in% ISO3),]
```

### Indicator_Id
```{r}
# Comprobation
setdiff(unique(GovData360$Indicator_Id), unique(GovData360IND$Indicator_Id))
GovData360 = GovData360[GovData360$Indicator_Id != "", ]

setdiff(unique(GovData360IND$Indicator_Id), unique(GovData360$Indicator_Id))
# There are indicators without values. Remove them.

diff = setdiff(unique(GovData360IND$Indicator_Id), unique(GovData360$Indicator_Id)) # list of indicators without data
GovData360IND = GovData360IND[!(GovData360IND$Indicator_Id %in% diff), ] # Remove indicators without data from the IND file

setdiff(unique(GovData360$Indicator_Id), unique(GovData360IND$Indicator_Id))
setdiff(unique(GovData360IND$Indicator_Id), unique(GovData360$Indicator_Id))
```

### Indicator_Name

'Indicator_Name' does not match either. This is because the cleaning system has been different in each file and dataset. It is not a big problem now because we have the Indicator_Id as an ID. 

```{r}
ID.match = GovData360IND[, c('Indicator_Id', 'Indicator_Name')]

drop_Indicator_Name = c('Indicator_Name')
GovData360 = GovData360[, !(names(GovData360) %in% drop_Indicator_Name)]
# Match 
GovData360 = merge(GovData360, ID.match, by = 'Indicator_Id', all = T)

# Comprobation
setdiff(unique(GovData360$Indicator_Name), unique(GovData360IND$Indicator_Name))
setdiff(unique(GovData360IND$Indicator_Name), unique(GovData360$Indicator_Name))
```

```{r write in csv}
# Write in csv
write.csv(GovData360IND, "GovData360IND.csv")
write.csv(GovData360, "GovData360.csv")
```

```{r}

```


