---
title: "R Notebook"
output: html_notebook
---
This markdown is the one in charge of preparing the dataset for cleaningz

```{r libraries, include=FALSE}
library(dplyr)
library(stringr)
```

**Step 1:** Read the files and understand what columns are needed to add or remove.

```{r Reading files, echo=FALSE}
library(dplyr)
# Read files
Data_Source = 'WGI'
file = paste("../Data preprocessed/", Data_Source,"/", Data_Source, ".csv", sep = "")
df = read.csv(file, sep = ",")
fileIND = paste("../Data preprocessed/", Data_Source,"/", Data_Source, "IND.csv", sep = "")
df_IND = read.csv(fileIND, sep = ",")
print(Data_Source)
print(paste0("df_IND --> ", dim(df_IND)[1], " x ", dim(df_IND)[2]))
colnames(df_IND)
print(paste0("df --> ", dim(df)[1], " x ", dim(df)[2]))
colnames(df)
head(df_IND)
head(df)
#View(df)
#View(df_IND)
```
**Step 2:** Drop empty columns and empty rows
```{r Drop unused columns}
# Drop unused columns
dropIND = c("Rank", "Category_11",  "Category_12",  "Category_13", "Category_14", "Category_15",  "Category_21",  "Category_22", "Category_23", "Category_24" ,"Category_25", "Category_31", "Category_32", "Category_33", "Category_34",  "New1", "New2", "New3","New4", "New5", "keyN")
df_IND = df_IND[ ,!(names(df_IND) %in% dropIND)]

drop = c('keyN', 'Indicator_Id')
df = df[ ,!(names(df) %in% drop)]

df = df %>% filter(question != '') # Remove empty question rows - impossible to match
```

**Step 3:** Create Unique identifier - Indicator_ID and Indicator
```{r}
# Create Indicator_Id 
df_IND = df_IND %>% mutate(Display_Name_number = row_number())
df_IND = df_IND %>% mutate(Indicator_Id = paste(Display_Name_number, Dataset, answer, sep = "-"))
dropIND = c("Display_Name_number")
df_IND = df_IND[ ,!(names(df_IND) %in% dropIND)] #drop the auxiliary column created

#Indicator
df_IND$Indicator = tolower(df_IND$Display_Name)
df_IND$Indicator = trimws(df_IND$Indicator, which = 'both')

df_IND = df_IND %>% mutate(Indicator = paste(Indicator, Dataset, answer, sep = "-"))

# # Indicator in df
df$Indicator = tolower(df$question)
df$Indicator = trimws(df$Indicator, which = 'both')

df = df %>% mutate(Indicator = paste(Indicator, dataset, answer, sep = "-"))

#Indicator_Id
df = merge(df, df_IND[,c('Indicator','Indicator_Id')], by = 'Indicator', all.x = T)
drop = c("indicator")
df = df[ ,!(names(df) %in% drop)]

# Check if all are matched
df[is.na(df$Indicator_Id == T), ]
df$Indicator_Id[!(df$Indicator_Id %in% df_IND$Indicator_Id)]
df$Indicator[!(df$Indicator %in% df_IND$Indicator)]
df_IND$Indicator_Id[!(df_IND$Indicator_Id %in% df$Indicator_Id)]
```

*******************************************************************************************************************

*******************************************************************************************************************

**Step 4:** Rescue the metadata from the hierarchy file and tokenize the Display.Name to make sure you can do correctly the left join later.

```{r}
Hierarchy = read.csv("../Data preprocessed/hierarchy.indicators 12.31.17.csv")
#Hierarchy = read.csv("../Data preprocessed/GovData360IND.csv", sep = ";")
#colnames(Hierarchy)[5] = c('Display.Name')
Hierarchy = Hierarchy %>% filter(Dataset == "Worldwide Governance Indicators")
#View(Hierarchy)

## Make similar Hierarchy$Indicator to match it with Hierarchy
Hierarchy$Display.Name = gsub("¥Ë_", "", Hierarchy$Display.Name)
Hierarchy$Indicator = tolower(Hierarchy$Display.Name)
Hierarchy$Indicator = trimws(Hierarchy$Indicator, which = 'both')

Hierarchy = Hierarchy %>% mutate(Indicator = paste(Indicator, "WGI", Value.Type.Slug, sep = "-"))
Hierarchy$Indicator = gsub("lower_bound", "Lower", Hierarchy$Indicator)
Hierarchy$Indicator = gsub("Percentile Rank", "Rank", Hierarchy$Indicator)
Hierarchy$Indicator = gsub("standard_error", "StdErr", Hierarchy$Indicator)
Hierarchy$Indicator = gsub("upper_bound", "Upper", Hierarchy$Indicator)

#Which of the indicators in 2018, do not match in 2017
#df_IND$Indicator[!(df_IND$Indicator %in% Hierarchy$Indicator)]
Hierarchy$Indicator[!(Hierarchy$Indicator %in% df_IND$Indicator)]
#df_IND$Indicator[!(df_IND$Indicator %in% Hierarchy$Indicator)] #Dropped indicators
```
The indicators that do not match is because they might be dropped in the past. In any case, we will bring them until the end. They will have the categories and some other columns empty in the final dataset. At the last minute, we will dropped them if it proceeds.

**Step 5:** Left join between df_IND and Hierarchy.

```{r}
Hierarchy = Hierarchy %>% select('Indicator', 'Display.Name', 'Value.Type.Slug','Value.Type.Descriptor', 'Units', 'Rank.1', "Category.1.1", "Category.1.2", "Category.1.3", "Category.1.4", "Category.1.5", "Rank.2", "Category.2.1", "Category.2.2", "Category.2.3", "Category.2.4", "Category.2.5", "Rank.3","Category.3.1", "Category.3.2", "Category.3.3", "Category.3.4", "Indicator.Code", "Indicator.ID")

# MERGE
Master_IND = merge(df_IND, Hierarchy, by.x = 'Indicator', all.x = T)

# Drop and rename Display name. (In this case we will use the one in Hierarchy because it is cleaner)
drop = c('Display.Name')
Master_IND = Master_IND[ ,!(names(Master_IND) %in% drop)]
#colnames(Master_IND)[6] = 'Display_Name'
View(Master_IND)
```

**Step 6:** Make sure the indicators in df_IND match in df
Because we have changed the names of the indicators, some of them would not match, but still the ID will match.

```{r}
# Which indicators of df_IND are not in df
setdiff(Master_IND$Indicator, df$Indicator)
setdiff(Master_IND$Indicator_Id, df$Indicator_Id)

# Which indicators of df are not in df_IND
setdiff(df$Indicator_Id, Master_IND$Indicator_Id)
setdiff(df$Indicator, Master_IND$Indicator)
```


**Step 7:** Make sure the columns of Master_IND you have, match with the ones you need.
```{r}
# Rename columns
colnames = colnames(Master_IND)
colnames = gsub('Value.Type.Slug', 'Value_Type_Slug', colnames)
colnames = gsub('Value.Type.Descriptor','Value_Type_Descriptor', colnames)
colnames = gsub('Rank.1','Rank_1', colnames)
colnames = gsub('Category.1.1','Category_11', colnames)
colnames = gsub('Category.1.2','Category_12', colnames)
colnames = gsub('Category.1.3','Category_13', colnames)
colnames = gsub('Category.1.4','Category_14', colnames)
colnames = gsub('Category.1.5','Category_15', colnames)
colnames = gsub('Rank.2','Rank_2', colnames)
colnames = gsub('Category.2.1','Category_21', colnames)
colnames = gsub('Category.2.2','Category_22', colnames)
colnames = gsub('Category.2.3','Category_23', colnames)
colnames = gsub('Category.2.4','Category_24', colnames)
colnames = gsub('Category.2.5','Category_25', colnames)
colnames = gsub('Rank.3','Rank_3', colnames)
colnames = gsub('Category.3.1','Category_31', colnames)
colnames = gsub('Category.3.2','Category_32', colnames)
colnames = gsub('Category.3.3','Category_33', colnames)
colnames = gsub('Category.3.4','Category_34', colnames)
colnames(Master_IND) = colnames

# Create empty columns
Master_IND$overlap = ''
Master_IND$Indicator_Code = ''
Master_IND$Description = ''

#Read final file from 2017
GovDataIND360 = read.csv("../Data preprocessed/GovData360IND.csv", sep = ";")

setdiff(colnames(Master_IND), colnames(GovDataIND360))
setdiff(colnames(GovDataIND360), colnames(Master_IND))
```

**Step 8:** Write in csv the result
```{r}
Name.file = paste0("Cleaned files/",Data_Source, ".csv")
Name.file_IND = paste0("Cleaned files/",Data_Source,"IND.csv")

write.csv(df, Name.file)
write.csv(Master_IND, Name.file_IND)
```






