---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

This is report explains all the variables in the Ingestions files of GovData360.
File used: INDICATORS file of the ingestion of Fall 2017

```{r}
library(dplyr)
setwd("C:/Users/wb533078/OneDrive - WBG/1 DATA UPDATE/Old Ingestion - GovData360 10172017")
file1 = "GovData360.csv"
file2 = "GovData360IND.csv"
Data = read.csv(file1, sep = ";")
DataIND = read.csv(file2, sep = ";")
```

# Indicators file
```{r}
nrow(DataIND)
ncol(DataIND)
head(DataIND)
```

## Overlap
```{r}
str(DataIND$overlap)
```

## Indicator_Id
**It has to be filled.**
```{r}
str(DataIND$Indicator_Id)
sum(DataIND$Indicator_Id == "") # Number of empty elements
```

## Indicator_Code
**It has to be filled.**
```{r}
str(DataIND$Indicator_Code)
sum(DataIND$Indicator_Code == "") # Number of empty elements
```

## Indicator_Name

```{r}
DataIND$Indicator_Name = as.character(DataIND$Indicator_Name)
str(DataIND$Indicator_Name)
```

## Display_Name

```{r}
DataIND$Display_Name = as.character(DataIND$Display_Name)
str(DataIND$Display_Name)
head(DataIND$Display_Name)
sum(DataIND$Description == "")
```


## Dataset
**It has to be filled.**
```{r}
str(DataIND$Dataset)
head(DataIND$Dataset)
sum(DataIND$Dataset == "") # Number of empty elements
```

## Value_Type_Slug
**It has to be filled.**
```{r}
str(DataIND$Value_Type_Slug)
sum(DataIND$Value_Type_Slug == "") # Number of empty elements
A = DataIND %>% group_by(Value_Type_Slug) %>% summarise(n = n()) %>% arrange(desc(n))
head(A, 20)
```

## Value_Type_Descriptor
**It has to be filled and it is always equal to Value_Type_Slug**
```{r}
str(DataIND$Value_Type_Descriptor)
sum(DataIND$Value_Type_Descriptor == "") # Number of empty elements
A = DataIND %>% group_by(Value_Type_Descriptor) %>% summarise(n = n()) %>% arrange(desc(n))
head(A, 20)

B = ifelse(DataIND$Value_Type_Descriptor == DataIND$Value_Type_Slug, 1, 0)
table(B)
```

## Units
**It has to be filled.**
```{r}
str(DataIND$Units)
sum(DataIND$Units == "") # Number of empty elements
A = DataIND %>% group_by(Units) %>% summarise(n = n()) %>% arrange(desc(n))
head(A, 20)
```

## Description
Majority are empty.
```{r}
str(DataIND$Description)
sum(DataIND$Description == "") # Number of empty elements
head(DataIND$Description, 10)
```

## Rank_1
**It has to be filled**
```{r}
str(DataIND$Rank_1)
sum(DataIND$Rank_1 == "") # Number of empty elements
head(DataIND$Rank_1, 10)
```

## Category_1 and subcategories
**It has to be filled**
```{r}
str(DataIND$Category_12)
print(unique(DataIND$Category_12))
sum(DataIND$Category_12 == "") # Number of empty elements
sum(is.na(DataIND$Category_13))
sum(is.na(DataIND$Category_14))
sum(is.na(DataIND$Category_15))
```

## Category_2 and subcategories
```{r}
str(DataIND$Category_21)
sum(DataIND$Category_21 != "")
sum(DataIND$Category_22 != "") # Elements with value
sum(is.na(DataIND$Category_13))
sum(is.na(DataIND$Category_14))

```

## Category_3 and subcategories
```{r}
str(DataIND$Category_31)
sum(DataIND$Category_31 != "")
sum(DataIND$Category_32 != "") # Elements with value
sum(is.na(DataIND$Category_33))
sum(is.na(DataIND$Category_34))

```

## Answer
**It has to be filled**
```{r}
str(DataIND$answer)
sum(DataIND$answer == "") # Number of empty elements
A = DataIND %>% group_by(answer) %>% summarise(n = n()) %>% arrange(desc(n))
head(A, 20)
```







